
# Boston Buoy Data Analysis
Congyao Duan


## 1.Instrution

### My understanding of the Question
  Over the past 50 years, the average global temperature has increased at the fastest rate in recorded history. Global warming occurs when carbon dioxide (CO2) and other air pollutants and greenhouse gases collect in the atmosphere and absorb sunlight and solar radiation that have bounced off the earth’s surface. Normally, this radiation would escape into space—but these pollutants, which can last for years to centuries in the atmosphere, trap the heat and cause the planet to get hotter. The perpose of our project is to find out if there is evidence of global warming in the data collected by a single weather buoy in the NOAA National Data Buoy Center.

### My Aproach
   
   First, I use R to clean and select the raw data.I chose ATMP and WTMP for analysis. Because these two sets of temperature data best reflect the related trends of global warming.I took the 12 o 'clock data every day, it can reduce the number of observations in my dataset  without reducing the amount of information in the data about the climate change question.
   Secondly, I use R to analysis the data. I do some exploratory research to get familiar with this data，but there is no obvious trend. 
   Then I use linear regression to analyze the data.

### How I orgnize the work
     
  I use R to clean and select the raw data.Then use R to analysis the data and draw a conclution.

## 2.Data Cleaning and Organizing

  There are a lot of outliers in this data, and a lot of variables that are not needed for this project. So do the data cleaning and processing before starting the project.In this part, I cleaned up the outliers and removed the variables that were not needed,leave only useful date and temperature data(ATMP&WTMP).I chose ATMP and WTMP for analysis. Because these two sets of temperature data best reflect the related trends of global warming.I took the 12 o 'clock data every day, it can reduce the number of observations in my dataset  without reducing the amount of information in the data about the climate change question.

  
```{r}
library(tidyverse)
library(stringr)
library(rstanarm)

url_1 <- "http://www.ndbc.noaa.gov/view_text_file.php?filename=mlrf1h"
url_2 <- ".txt.gz&dir=data/historical/stdmet/"
years <- c(1999:2018)
urls <- str_c(url_1, years, url_2, sep = "")
filenames <- str_c("mr", years, sep = "")


# Year 1999 - 2006
for(i in 1:8){
  suppressMessages(
    # Fill any missing values with NA:
    assign(filenames[i], read.table(urls[i], header = TRUE, fill = TRUE))
  )
  
}
# Year 2007 - 2018
for(i in 9:20){
  suppressMessages(
    # Fill any missing values with NA and use the same column names as year 2006
    assign(filenames[i], read.table(urls[i], header = FALSE, 
                                    fill = TRUE, col.names = colnames(mr2006))),
  )
  
}

```


```{r}
#use loops to get rid of the excess columns
mr1999$TIDE <- NA
n <- length(urls)
for (i in 1:n){
  file <- get(filenames[i])
  colnames(file)[1] <-"YYYY"
  if(ncol(file) == 18){
    file <- subset(file, select = -mm )
  }
  if(i == 1){
    MR <- file
  }else{
    MR <- rbind.data.frame(MR, file)
  }
  
}


```


```{r}
#Get rid of the excess columns
i<-2005
repeat { 
  assign(paste("mr",as.character(i),sep=""),
         get(paste("mr",as.character(i),sep=""))[,-5])
  i=i+1
  if(i>2018)
  {break}
}

```



```{r}
#screen out data at 12 o'clock
i<-1999
repeat { 
  assign(paste("mr",as.character(i),sep=""),get(paste("mr",as.character(i),sep=""))[which(get(paste("mr",as.character(i),sep=""))$hh == 12), ])
  i=i+1
  if(i>2018)
  {break}
}

```


```{r}
#Find out outliers
mr1999$TIDE <- NA
n <- 20
for (i in 1:n){
  file <- get(filenames[i])
  colnames(file)[1] <-"YYYY"
  if(i == 1){
    MRC <- file
  }else{
    MRC <- rbind.data.frame(MRC, file)
  }
  
}

#Get rid of the useless columns
MRC<-MRC[c(1,2,3,13,14)]
```

```{r}
#clean up abnormal data
MRC$ATMP[which(MRC$ATMP>=100)]=NA
MRC$WTMP[which(MRC$WTMP>=100)]=NA
MRC=na.omit(MRC)
```


## 3.Exploratory Data Analysis(EDA)
 
   In order to see the distruction of the data clearly,I draw boxplots and violin plots to observe first.Boxplot can not only reflect the distribution characteristics of the original data, but also compare the distribution characteristics of multiple groups of data. It can find the maximum, minimum, median and two quartiles of the data. A boxplot can also be used to find outliers and thus process outliers in data.Violin plots are used to show the distribution and probability density of multiple sets of data. This chart combines the features of box and density charts and is mainly used to show the distribution shape of the data. Similar to the box diagram, but better displayed at the density level.
  
  
```{r}
#Draw boxplots
MRC$YYYY[which(MRC$YYYY==1999)]="1999y"
ggplot(data=MRC,aes(x=YYYY,y=ATMP))+geom_boxplot()
ggplot(data=MRC,aes(x=YYYY,y=WTMP))+geom_boxplot()

```

```{r}
#Draw violin plots
ggplot(data=MRC,aes(x=YYYY,y=ATMP))+geom_violin()
ggplot(data=MRC,aes(x=YYYY,y=WTMP))+geom_violin()

```
   
   By observing the boxplot and violin plot, it was found that no obvious temperature trend could be observed. There was no significant trend in the median, maximum and minimum values. The data fluctuated, and the graph and the distribution of the data did not reveal the relationship between temperature and year.In order to find the relationship between temperature and time, we need to do further research.



## 4.Method

   Linear regression can determine the quantitative relationship of interdependence between two or more variables. The density of linear regression can draw a trend line, which represents the long-term trend of time series data. It tells us whether a particular set of data has increased or decreased over a period of time. Although we can visually observe the position of the data points in the coordinate system to roughly draw the trend line, it is more appropriate to use linear regression to calculate the position and slope of the trend line.
                    
                    
```{r}
#draw scatter diagram and regression lines of the average temperature
datamean=group_by(MRC,YYYY)%>%summarize_each(funs(mean))
x=c(1999,2000,2001,2002,2003,2004,2005,2006,2007,2008,2009,2010,2011,2012,2013,2014,2015,2016,2017,2018)
y<-datamean$ATMP
z<-datamean$WTMP
fit_1<-stan_glm(y~x)
plot(datamean$YYYY, datamean$ATMP, main="Data and fitted regression line")
abline(fit_1)
print(fit_1)
coef(fit_1)
fit_2<-stan_glm(z~x)
plot(datamean$YYYY, datamean$WTMP, main="Data and fitted regression line")
abline(fit_2)
print(fit_2)
coef(fit_2)
```

   
#### First, we calculate the average temperature of each year  and draw a scatter plot of the average. And make linear regression model.The regression equation with one variable is obtained：
               
                ATMP(mean)=18.181+0.0032*year+error
                WTMP(mean)=14.475+0.00597*year+error
#### Then we draw the regression line in the scatter plot.



```{r}
#Select the highest temperature of the year(12 o'clock)
#draw scatter diagram and regression lines of the max temperature
datamax=group_by(MRC,YYYY)%>%summarize_each(funs(max))
p<-datamax$ATMP
plot(datamax$YYYY, datamax$ATMP, main="Data and fitted regression line")
fit_3<-stan_glm(p~x)
abline(fit_3)
print(fit_3)
coef(fit_3)
q<-datamax$WTMP
plot(datamax$YYYY, datamax$WTMP, main="Data and fitted regression line")
fit_4<-stan_glm(q~x)
abline(fit_4)
print(fit_4)
coef(fit_4)
```
   
#### Second , we calculate the highest temperature of each year  and draw a scatter plot of the max. And make linear regression model.The regression equation with one variable is obtained：
                 
                 ATMP(max)=-6.975+0.01828*year+error
                 WTMP(max)=28.8025+0.00087*year+error
#### Then we draw the regression line in the scatter plot.
   
   
```{r}
#Select the lowest temperature of the year(12 o'clock)
#draw scatter diagram and regression lines of the min temperature
datamin=group_by(MRC,YYYY)%>%summarize_each(funs(min))
r<-datamin$ATMP
plot(datamin$YYYY, datamin$ATMP, main="Data and fitted regression line")
fit_5<-stan_glm(r~x)
abline(fit_5)
print(fit_5)
coef(fit_5)
s<-datamin$WTMP
plot(datamin$YYYY, datamin$WTMP, main="Data and fitted regression line")
fit_6<-stan_glm(s~x)
abline(fit_6)
print(fit_6)
coef(fit_6)
```

#### At last , we calculate the lowest temperature of each year  and draw a scatter plot of the min. And make linear regression model.The regression equation with one variable is obtained：

              ATMP(min)=-177.5036+0.0927*year+error
              WTMP(min)=-108.5465+0.0643*year+error
#### Then we draw the regression line in the scatter plot.


## 5.Discussion of the Problem(My conclution)

  Through the above studies, we have the boxplot/violin plots.And found their linear regression relationship:
                    
            ATMP(mean)=18.181+0.0032*year+error
            WTMP(mean)=14.475+0.00597*year+error
            ATMP(max)=-6.975+0.01828*year+error
            WTMP(max)=28.8025+0.00087*year+error
            ATMP(min)=-177.5036+0.0927*year+error
            WTMP(min)=-108.5465+0.0643*year+error
                    
  We can find out that the temperature has a tendency to increase over time, but it's not obvious.I don't think that this is a result that tells you that temperature is related to the realization of the year, or that the temperature is going to increase over time in just 20 years.
  I think a time series model would be more appropriate for these data (but I haven't studied it).Or maybe we should take a longer time frame. And the study  can 10 years as a unit of time rather than a year,because temperature change is a very slow process.In this way, the relationship between temperature and time will be more significant, which is convenient for us to study and get a clear conclusion.


## 6.Reference

package:https://cran.r-project.org/web/packages/citation/index.html
links：https://www.cnblogs.com/sylvanas2012/p/4328861.html
       https://www.ndbc.noaa.gov/station_page.php?station=44013
       http://www.mamicode.com/info-detail-1662071.html
       https://bbs.pinggu.org/forum.php?mod=viewthread&tid=6612706
